---
title: "WUP_04_Alt"
author: "Rita Jarbanda"
date: "fall 2023"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
mydata<-read.csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and the RACE of the person taking the test   
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two different RACES

# Methods

<!--Mention that you intend to use chatGPT to the greatest extent possible. Give credit to chatGPT when you use it to create code in your report. Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

```{r eval=FALSE}
mydata <- mydata %>%
mutate(across(where(is.character), as.factor))
```
We change all the character variable to factor variables.The type of this problem needs a numerical variable called WORDSUM and a factor variable called RACE. We will be using a group of helper files to help us complete the analysis og Numerical and factorial variables.
# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
basicCN <- ggplot(mydata,aes(x=RACE,y=WORDSUM))

basicCN + geom_boxplot()
```

By looking at the box plot graph, its not clear enough if there is a significant difference between the WHITE and other RACES. It also not clear is there is a difference between the BLACK and other RACES 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~RACE,data=mydata)
```

By looking at the favstats, the average values between BLACK and WHITE are very close however the mean value for the OTHER race is have a lower value meaning that there is a difference between between the OTHER and both the WHITE and BLACK races

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~RACE,data=mydata)
summary.aov(model1)
```
P-value= 0.0182

By looking at the one way anova test, our p-value is less than 0.5 we can conclude that we need to run one more test to be able to analyze the data.  

```{r}
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model1),las=2)
```

By looking at the multiple corporation test, we can see that the zero confidence level intersect with the OTHER-BLACK  and the WHITE-BLACK that there is no difference in the average scores in the WORDSUM test between each pair of these races. However the zero confidence level dos not intersect with the WHITE-OTHER which means that there is difference in the average scores between these races and that's cause cur p-value to be small.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
